Road User video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-07-25 paper.qmd
Brake ref

```{r}
#| label: tbl-raw
#| tbl-cap: "Random sample of 5 records from the raw data."
set.seed(24)
d_all |>
  sample_n(5) |>
  select(-district, -`offence_code`) |>
  mutate(date = as.Date(date)) |>
  arrange(date) |>
  rename_all(snakecase::to_title_case) |>
  knitr::kable()

  # |>
  # # Striped styling and tiny text to fit:
  # kableExtra::kable_styling(latex_options = "striped") |>
  # # Set column widths:
  # kableExtra::column_spec(1, width = "3em") |>
  # kableExtra::column_spec(2, width = "3em") |>
  # kableExtra::column_spec(3, width = "3em") |>
  # kableExtra::column_spec(4, width = "3em") |>
  # kableExtra::column_spec(5, width = "9em") |>
  # kableExtra::column_spec(6, width = "4em") |>
  # kableExtra::column_spec(8, width = "8em")
```

>>>>

```{r}
#| label: tbl-raw
#| tbl-cap: "Random sample of 5 records from the raw data."
set.seed(24)
d_all |>
  sample_n(5) |>
  select(-district, -`offence_code`) |>
  mutate(date = as.Date(date)) |>
  arrange(date) |>
  rename_all(snakecase::to_title_case) |>
  knitr::kable() |>
  # Striped styling and tiny text to fit:
  kableExtra::kable_styling(latex_options = "striped") |>
  # Set column widths:
  kableExtra::column_spec(1, width = "3em") |>
  kableExtra::column_spec(2, width = "3em") |>
  kableExtra::column_spec(3, width = "3em") |>
  kableExtra::column_spec(4, width = "3em") |>
  kableExtra::column_spec(5, width = "9em") |>
  kableExtra::column_spec(6, width = "4em") |>
  kableExtra::column_spec(8, width = "8em")
```
